---
title: "stats"
author: "Kyla Perocho"
date: "2026-07-22"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

```{r}
# ============================================================================
# CHROMOSOME ONE ONLY 
#
# FULL ANALYSIS: Nucleotide diversity (pi) as a function of sample size and
# number of loci -- EDA, ANOVA, effects/interaction plots, diagnostics, RSM,
# hypothesis testing, and optimal design point identification.
#
# Required packages:
#   install.packages(c("rsm", "ggplot2"))
# (car is NOT required -- Levene's test and Type II-style ANOVA equivalents
# are done with base R below, in case 'car' fails to install due to missing
# CMake for its nloptr/lme4 dependencies)
#
# Set seed and Directory
# ============================================================================
```

## Directory

```{r}
getwd()
setwd("C:/Users/Kyla Perocho/Downloads")
```

## Libraries

```{r}
library(rsm)
library(ggplot2)   # for polished EDA plots
library(knitr)
library(scatterplot3d)
library(dplyr)
library(car)
library(tseries)
library(nortest)
library(rstatix)
```

set.seed(42)

# STEP 0: LOAD DATA

```{r}
# BASELINE

baseline <- read.csv("pi values - true pi.csv") 
true_pi <- baseline$pi_per_site[baseline$chromosome == "chr1"]

# SAMPLE
data <- read.csv("pi values - final_compiled_pi.csv")

# PSEUDO  BASELINE
# Filter for n_indiv == 100 & loci == 150/300, then compute the mean
pseudo_true_pi <- data %>%
  filter(n_indiv == 100, loci == 300) %>%
  summarise(pseudo_true_pi = mean(avg_pi, na.rm = TRUE)) %>%
  pull(pseudo_true_pi)
```

## STEP 1: EXPLORATORY DATA ANALYSIS (EDA)

EDA: Data structure
```{r}
str(data) 
```
EDA: Replicates per design
```{r}
print(table(distinct$n_indiv, distinct$loci))
```

EDA: Summary statistics
```{r}
summary(data)
```

EDA: Mean/SD pi per design point

```{r}
eda_summary <- aggregate(avg_pi ~ n_indiv + loci, data = data,
                         FUN = function(x) c(mean = mean(x), sd = sd(x), n = length(x)))
kable(eda_summary)
```

EDA Plot 1: Faceted boxplot -- both factors shown together
```{r}
p1 <- ggplot(data, aes(x = n_indiv, y = avg_pi)) +
  geom_violin(fill = "orange", alpha = 0.6) +
  geom_hline(yintercept = true_pi, color = "red", linetype = "dashed") +
  facet_wrap(~ loci, labeller = label_both, nrow=1) +
  labs(title = "Pi distribution: sample size & loci count (faceted)",
       x = "Sample size (n)", y = "Nucleotide diversity (pi)") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
print(p1)
```

EDA Plot 2: 2D Scatterplot

```{r}
p2 <- scatterplot3d(data[c("n_indiv", "loci", "avg_pi")],
                    main="3D Scatter Plot",
                    xlab = "Indiv",
                    ylab = "Loci",
                    zlab = "Pi")
```

EDA Plot 3: Overall distribution (histogram/density) of pi estimates

```{r}
p3 <- ggplot(data, aes(x = n_indiv, y = avg_pi)) +
  geom_point(fill = "orange", alpha = 0.6) +
  geom_hline(yintercept = true_pi, color = "red", linetype = "dashed")
  labs(title = "Pi distribution: sample size x loci count (faceted)",
       x = "Sample size (n)", y = "Nucleotide diversity (pi)") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
print(p3)


p4 <- ggplot(data, aes(x = avg_pi)) +
  geom_histogram(aes(y = after_stat(density)), bins = 40, fill = "gray70", color = "white") +
  geom_density(color = "blue", linewidth = 1) +
  geom_vline(xintercept = true_pi, color = "red", linetype = "dashed", linewidth = 1) +
  labs(title = "Overall distribution of pi estimates (all design points combined)",
       x = "Nucleotide diversity (pi)", y = "Density") +
  theme_minimal()
print(p4)
```
EDA INTERPRETATION:
- Every single row for loci 150 through 300 is an exact duplicate down to the last decimal point across all n_indiv levels (1, 2, 3, 4, 5, 10, 20, 30, 50, 100). Which makes sense kasi each sample is 1 chromosome with 150 loci from 100 indiv, so greater than 150 loci values repeats.

-  n=1 cannot measure within-sample pairwise diversity effectively, causing pi to drop near zero and affects the data by skewing it heavily to the left.

- we have trimodal distribution, caused by n=1, then our "normal values of loci x indiv", then the duplicates from 150-300 loci.

But let's say we proceeded with the analysis without cleaning the data, ie, removing n=1 and subsetting to 2-150 indiv only

## STEP 2: TWO-ANOVA AND DIAGNOSTIC PLOTS
Ho: (main effect n_samples): mean pi is the same across all sample sizes
Ho: (main effect n_loci): mean pi is the same across all loci counts
Ho :(interaction): the effect of sample size on pi does not

```{r}
# Model
model_anova <- aov(avg_pi ~ n_indiv * loci, data = data)
print(summary(model_anova))
```


```{r}
# Main Effects
main_eff_samples <- aggregate(avg_pi ~ n_indiv, data = data, FUN = mean)
main_eff_loci    <- aggregate(avg_pi ~ loci, data = data, FUN = mean)

par(mfrow = c(1, 2))
plot(main_eff_samples$n_indiv, main_eff_samples$avg_pi, type = "b", pch = 19,
     xlab = "Sample size", ylab = "Mean pi", main = "Main effect: sample size")
abline(h = true_pi, col = "red", lty = 2)

plot(main_eff_loci$loci, main_eff_loci$avg_pi, type = "b", pch = 19, col = "darkgreen",
     xlab = "Number of loci", ylab = "Mean pi", main = "Main effect: loci")
abline(h = true_pi, col = "red", lty = 2)
par(mfrow = c(1, 1))
```


```{r}
# Interaction Effect
interaction.plot(
  x.factor = data$n_indiv, trace.factor = data$loci,
  response = data$avg_pi, fun = mean,
  type = "b", pch = 19, col = rainbow(length(unique(data$loci))),
  xlab = "Sample size", ylab = "Mean pi", trace.label = "loci",
  main = "Interaction Plot: sample size x loci"
)
abline(h = true_pi, col = "red", lty = 2)
```


```{r}
# Diagnostic Plots
par(mfrow = c(2, 2))
plot(model_anova)
par(mfrow = c(1, 1))
```


```{r}
# Normality Test
shapiro_result <- shapiro.test(residuals(model_anova))
print(shapiro_result)
```


```{r}
# Heteroscedasticity Test (Levene's Test)
manual_levene_test <- function(y, group) {
  group <- factor(group)
  medians <- tapply(y, group, median)
  abs_dev <- abs(y - medians[group])
  fit <- aov(abs_dev ~ group)
  summary(fit)
}

group_combo <- interaction(data$n_indiv, data$loci)
levene_result <- manual_levene_test(data$avg_pi, group_combo)
cat("\nLevene's test for homogeneity of variance (manual base-R version):\n")
print(levene_result)
levene_p <- levene_result[[1]]$"Pr(>F)"[1]

# using car package
# leveneTest(avg_pi ~ factor(n_indiv) * factor(loci), data = data)
```

# GET DISTINCT COMBINATION VALUES
```{r}
distinct <- data %>%
  filter(loci %in% c(30, 60, 90, 120, 150),
         n_indiv > 1)
```
## STEP 1: EXPLORATORY DATA ANALYSIS (EDA)

EDA: Mean/SD pi per design point
```{r}
eda_summary <- aggregate(avg_pi ~ n_indiv + loci, data = distinct,
                         FUN = function(x) c(mean = mean(x), sd = sd(x), n = length(x)))
kable(eda_summary)
```

EDA Plot 1: Faceted boxplot -- both factors shown together
```{r}
p1 <- ggplot(distinct, aes(x = n_indiv, y = avg_pi)) +
  geom_violin(fill = "orange", alpha = 0.6) +
  geom_hline(yintercept = true_pi, color = "red", linetype = "dashed") +
  facet_wrap(~ loci, labeller = label_both, nrow=1) +
  labs(title = "Pi distribution: sample size & loci count (faceted)",
       x = "Sample size (n)", y = "Nucleotide diversity (pi)") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
print(p1)
```

EDA Plot 2: 2D Scatterplot

```{r}
p2 <- scatterplot3d(distinct[c("n_indiv", "loci", "avg_pi")],
                    main="3D Scatter Plot",
                    xlab = "Indiv",
                    ylab = "Loci",
                    zlab = "Pi")
```

EDA Plot 3: Overall distribution (histogram/density) of pi estimates

```{r}
p3 <- ggplot(distinct, aes(x = n_indiv, y = avg_pi)) +
  geom_point(fill = "orange", alpha = 0.6) +
  geom_hline(yintercept = true_pi, color = "red", linetype = "dashed")
  labs(title = "Pi distribution: sample size x loci count (faceted)",
       x = "Sample size (n)", y = "Nucleotide diversity (pi)") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
print(p3)


p4 <- ggplot(distinct, aes(x = avg_pi)) +
  geom_histogram(aes(y = after_stat(density)), bins = 40, fill = "gray70", color = "white") +
  geom_density(color = "blue", linewidth = 1) +
  geom_vline(xintercept = true_pi, color = "red", linetype = "dashed", linewidth = 1) +
  labs(title = "Overall distribution of pi estimates (all design points combined)",
       x = "Nucleotide diversity (pi)", y = "Density") +
  theme_minimal()
print(p4)
```
## STEP 2: TWO-WAY ANOVA (factorial, treating n_indiv & loci as categorical)
Ho: (main effect n_samples): mean pi is the same across all sample sizes
Ho: (main effect n_loci): mean pi is the same across all loci counts
Ho :(interaction): the effect of sample size on pi does not
```{r}
distinct_anova <- aov(avg_pi ~ n_indiv * loci, data = distinct) # Type I
summary(distinct_anova)
```
## STEP 3: EFFECTS PLOTS & INTERACTION PLOT
```{r}
# Main effects plots (marginal means for each factor individually)
main_eff_samples <- aggregate(avg_pi ~ n_indiv, data = distinct, FUN = mean)
main_eff_loci    <- aggregate(avg_pi ~ loci, data = distinct, FUN = mean)

par(mfrow = c(1, 2))
plot(main_eff_samples$n_indiv, main_eff_samples$avg_pi, type = "b", pch = 19,
     xlab = "Sample size", ylab = "Mean pi", main = "Main effect: sample size")
abline(h = true_pi, col = "red", lty = 2)

plot(main_eff_loci$loci, main_eff_loci$avg_pi, type = "b", pch = 19, col = "darkgreen",
     xlab = "Number of loci", ylab = "Mean pi", main = "Main effect: loci")
abline(h = true_pi, col = "red", lty = 2)
par(mfrow = c(1, 1))
```


```{r}
# Interaction Effect
interaction.plot(
  x.factor = distinct$n_indiv, trace.factor = distinct$loci,
  response = distinct$avg_pi, fun = mean,
  type = "b", pch = 19, col = rainbow(length(unique(distinct$loci))),
  xlab = "Sample size", ylab = "Mean pi", trace.label = "loci",
  main = "Interaction Plot: sample size x loci"
)
abline(h = true_pi, col = "red", lty = 2)
```

## STEP 4: DIAGNOSTIC TESTS (residual diagnostics for the ANOVA model)
```{r}
# Diagnostic Plots
par(mfrow = c(2, 2))
plot(distinct_anova)
par(mfrow = c(1, 1))
```


```{r}
# Normality Test (Shapiko-Wilk)
shapiro_result <- shapiro.test(residuals(distinct_anova))
print(shapiro_result)

# Other Tests (Jacque-Bera, Anderson-Darling)
jarque.bera.test(residuals(distinct_anova))
ad.test(residuals(distinct_anova))
```

```{r}
# Heteroscedasticity Test (Levene's Test)
manual_levene_test <- function(y, group) {
  group <- factor(group)
  medians <- tapply(y, group, median)
  abs_dev <- abs(y - medians[group])
  fit <- aov(abs_dev ~ group)
  summary(fit)
}

group_combo <- interaction(distinct$n_indiv, distinct$loci)
levene_result <- manual_levene_test(distinct$avg_pi, group_combo)
cat("\nLevene's test for homogeneity of variance (manual base-R version):\n")
print(levene_result)
levene_p <- levene_result[[1]]$"Pr(>F)"[1]

# using car package
# leveneTest(log(avg_pi) ~ factor(n_indiv) * factor(loci), data = distinct)
```

Since we have heteroscedastic model, we do correction for the model we will use in hypothesis testing
```{r}
distinct_anova2 <- Anova(distinct_anova, type = "II", white.adjust = "hc3")
distinct_anova2
```

```{r}
# Post Hoc

## Main effects (indiv)
gh_n_indiv <- distinct %>%
  games_howell_test(avg_pi ~ n_indiv)

print(gh_n_indiv)

## Main effects (loci)
gh_loci <- distinct %>%
  games_howell_test(avg_pi ~ loci)

print(gh_loci)

## Interaction
interaction <- distinct %>%
  mutate(group = interaction(n_indiv, loci, sep = "_"))

gh_interaction <- interaction %>%
  games_howell_test(avg_pi ~ group)

print(gh_interaction)

# summary
lowest_n_indiv <- gh_n_indiv %>%
  filter(p.adj == min(p.adj))

lowest_loci <- gh_loci %>%
  filter(p.adj == min(p.adj))

lowest_int <- gh_interaction %>%
  filter(p.adj == min(p.adj))

rbind(lowest_n_indiv,  lowest_loci, lowest_int)

```

## STEP 5: RSM ANALYSIS (response surface regression, continuous factors)
```{r}
data_coded <- coded.data(
  distinct,
  x1 ~ (n_indiv - mean(range(distinct$n_indiv))) / (diff(range(distinct$n_indiv)) / 2),
  x2 ~ (loci    - mean(range(distinct$loci)))    / (diff(range(distinct$loci)) / 2)
)

model_FO <- rsm(avg_pi ~ FO(x1, x2), data = data_coded)
model_SO <- rsm(avg_pi ~ SO(x1, x2), data = data_coded)

# RSM: FIRST-ORDER MODEL
summary(model_FO)

# RSM: SECOND-ORDER MODEL
summary(model_SO)
```
INTERPRETATION:
kahit na may lack of fit siya, SO can already present the 77% of the total variation
optimal: ~65, ~76

from then on, increasing can actually diminish the power of estimating the true pi

```{r}
# response surface visualizations
persp(model_SO, x1 ~ x2, col = "lightblue", contours = "colors",
      xlabs = c("Sample size (coded)", "Number of loci (coded)"),
      zlab = "Estimated pi", main = "Response Surface: pi vs sample size x loci")

contour(model_SO, x1 ~ x2,
        xlabs = c("Sample size (coded)", "Number of loci (coded)"),
        main = "Contour Plot: pi response surface")

image(model_SO, x1 ~ x2,
      xlabs = c("Sample size (coded)", "Number of loci (coded)"),
      main = "Heatmap: pi response surface")
```
# STEP 6: n=2 ADEQUACY HYPOTHESIS TEST (bootstrap RMSE)
Ho: RMSE(n=2) >= $\delta$ * true_pi  (n=2 is NOT adequate)
Ha: RMSE(n=2) < $\delta$ true_pi  (n=2 IS adequate)

```{r}
# Define your acceptable error threshold (e.g., 10% of true_pi) delta
delta <- 35  # Change to 5, 10, or 15 based on study strictness

bootstrap_rmse_test <- function(estimates, true_value, threshold_pct = 10, n_boot = 10000) {
  n <- length(estimates)
  
  # Absolute threshold value (e.g., 10% of true_pi)
  threshold_val <- true_value * (threshold_pct / 100)
  
  boot_rmse <- numeric(n_boot)
  for (i in 1:n_boot) {
    resampled <- sample(estimates, size = n, replace = TRUE)
    boot_rmse[i] <- sqrt(mean((resampled - true_value)^2))
  }
  
  observed_rmse <- sqrt(mean((estimates - true_value)^2))
  
  # One-tailed test: Probability that true RMSE is GREATER THAN OR EQUAL TO threshold
  p_value <- mean(boot_rmse >= threshold_val)
  ci <- quantile(boot_rmse, c(0.025, 0.975))
  
  list(
    observed_rmse = observed_rmse, 
    observed_rmse_pct = 100 * (observed_rmse / true_value),
    threshold_val = threshold_val,
    threshold_pct = threshold_pct,
    ci_lower = ci[1], 
    ci_upper = ci[2], 
    p_value = p_value, 
    reject_h0 = p_value < 0.05
  )
}

# Run the test against Chromosome 1 true_pi
n2_estimates <- distinct$avg_pi[distinct$n_indiv == 2]
n2_test <- bootstrap_rmse_test(n2_estimates, true_pi, threshold_pct = delta)

cat("\n=== n=2 ADEQUACY HYPOTHESIS TEST ===\n")
cat("Chromosome 1 True Pi:", true_pi, "\n")
cat("Observed RMSE:", n2_test$observed_rmse, "(", round(n2_test$observed_rmse_pct, 2), "% of true pi)\n")
cat("Target Threshold:", n2_test$threshold_val, "(", n2_test$threshold_pct, "% of true pi)\n")
cat("Bootstrap p-value:", n2_test$p_value, "\n")
cat("Decision:", ifelse(n2_test$reject_h0,
                        "REJECT H0 -> n=2 IS adequate (RMSE is significantly < threshold)",
                        "FAIL TO REJECT H0 -> n=2 is NOT adequate (RMSE >= threshold)"), "\n")
```

# STEP 7: OPTIMAL DESIGN POINT (cost-aware, within adequacy tolerance)
```{r}
# 1. Define target RMSE threshold based on your acceptable error percentage
target_rmse_threshold <- true_pi * (delta / 100)

# -----------------------------------------------------------------------------
# A. EMPIRICAL BEST (from actual tested design combinations)
# -----------------------------------------------------------------------------
# Calculate observed RMSE for each empirical combination of n_indiv and loci
agg_emp <- aggregate(avg_pi ~ n_indiv + loci, data = distinct, FUN = function(x) {
  sqrt(mean((x - true_pi)^2)) # Empirical RMSE
})
colnames(agg_emp)[3] <- "observed_rmse"

# Filter for adequate empirical combinations (RMSE <= target_rmse_threshold)
adequate_empirical <- agg_emp[agg_emp$observed_rmse <= target_rmse_threshold, ]

if (nrow(adequate_empirical) > 0) {
  adequate_empirical$cost <- adequate_empirical$n_indiv + adequate_empirical$loci
  best_empirical <- adequate_empirical[which.min(adequate_empirical$cost), ]
} else {
  # If no point meets strict adequacy, pick the one with lowest overall RMSE
  best_empirical <- agg_emp[which.min(agg_emp$observed_rmse), ]
  warning("No empirical design point met the strict RMSE threshold. Returning lowest RMSE point.")
}

# -----------------------------------------------------------------------------
# B. MODEL-BASED OPTIMAL POINT (searches the fitted RSM surface)
# -----------------------------------------------------------------------------
# Create fine grid across coded space (-1 to +1)
grid <- expand.grid(
  x1 = seq(-1, 1, length.out = 200),
  x2 = seq(-1, 1, length.out = 200)
)

# Predict pi from Second-Order RSM model
grid$predicted_pi <- predict(model_SO, newdata = grid)

# Convert predicted bias into estimated prediction error (RMSE proxy)
grid$predicted_rmse <- abs(grid$predicted_pi - true_pi)

# Uncode x1 and x2 back to original scale (n_indiv and loci)
grid$n_indiv <- grid$x1 * (diff(range(distinct$n_indiv)) / 2) + mean(range(distinct$n_indiv))
grid$loci    <- grid$x2 * (diff(range(distinct$loci))    / 2) + mean(range(distinct$loci))

# Filter grid for points that satisfy ADEQUACY (Predicted RMSE <= Target Threshold)
adequate_grid <- grid[grid$predicted_rmse <= target_rmse_threshold, ]

if (nrow(adequate_grid) > 0) {
  # Calculate cost (Adjust weights here if sequencing individuals costs more than loci)
  adequate_grid$cost <- adequate_grid$n_indiv + adequate_grid$loci
  
  # Pick the point with the lowest cost among all adequate points
  best_model_based <- adequate_grid[which.min(adequate_grid$cost), ]
} else {
  # If no point on the surface meets adequacy, pick the minimum error point on the surface
  best_model_based <- grid[which.min(grid$predicted_rmse), ]
  warning("No RSM surface point met the strict RMSE threshold. Returning minimum error point.")
}

# -----------------------------------------------------------------------------
# PRINT RESULTS
# -----------------------------------------------------------------------------
cat("\n=== OPTIMAL DESIGN POINT SELECTION ===\n")
cat("Target RMSE Threshold (", delta, "% of true pi):", round(target_rmse_threshold, 6), "\n\n")

cat("--> Empirical Cheapest-Adequate Point:\n")
cat("    n_indiv:", round(best_empirical$n_indiv, 1), 
    "| loci:", round(best_empirical$loci, 1), 
    "| RMSE:", round(best_empirical$observed_rmse, 6), "\n\n")

cat("--> RSM Model-Based Cheapest-Adequate Point:\n")
cat("    n_indiv:", round(best_model_based$n_indiv, 1), 
    "| loci:", round(best_model_based$loci, 1), 
    "| Predicted RMSE:", round(best_model_based$predicted_rmse, 6), "\n")
```


```{r}
# =============================================================================
# STEP 8: CONSOLIDATED SUMMARY TABLE (Safe Type II ANOVA Extraction)
# =============================================================================

# Convert Type II ANOVA object to a standard data frame to extract p-values safely
anova_df <- as.data.frame(distinct_anova2)

# Helper function to extract p-value for a given term without crashing
get_p_val <- function(df, row_pattern) {
  row_idx <- grep(row_pattern, rownames(df), ignore.case = TRUE)[1]
  if (is.na(row_idx)) return(NA)
  p_col <- grep("Pr|p", colnames(df), ignore.case = TRUE)[1]
  return(as.numeric(df[row_idx, p_col]))
}

# Extract p-values for main effects and interaction
p_n_indiv <- get_p_val(anova_df, "^n_indiv$")
p_loci    <- get_p_val(anova_df, "^loci$")
p_int     <- get_p_val(anova_df, "n_indiv:loci|n_indiv\\*loci")

# Safe helper for p-value formatting
fmt_p <- function(val) {
  if (is.null(val) || is.na(val)) return("-")
  return(signif(val, 4))
}

summary_table <- data.frame(
  Item = c(
    "ANOVA: main effect of n_indiv (p-value)",
    "ANOVA: main effect of loci (p-value)",
    "ANOVA: interaction n_indiv x loci (p-value)",
    "Shapiro-Wilk normality test (p-value)",
    "Levene's test for equal variance (p-value)",
    "RSM model adequacy test (FO vs SO, p-value)",
    "  -> Decision",
    "n=2 adequacy test (bootstrap RMSE, p-value)",
    "  -> Decision",
    "Best EMPIRICAL design point: n_indiv",
    "Best EMPIRICAL design point: loci",
    "Best EMPIRICAL design point: abs. diff from true pi",
    "Best COST-AWARE design point: n_indiv",
    "Best COST-AWARE design point: loci",
    "Best COST-AWARE design point: abs. diff from true pi"
  ),
  Value = c(
    fmt_p(p_n_indiv),
    fmt_p(p_loci),
    fmt_p(p_int),
    fmt_p(shapiro_result$p.value),
    fmt_p(levene_p),
    fmt_p(p_val),
    ifelse(!is.na(p_val) && p_val < 0.05, "Second-order model needed", "First-order model adequate"),
    fmt_p(n2_test$p_value),
    ifelse(n2_test$reject_h0, "n=2 IS adequate", "n=2 is NOT adequate"),
    best_empirical$n_indiv,
    best_empirical$loci,
    signif(ifelse(!is.null(best_empirical$abs_diff), best_empirical$abs_diff, best_empirical$observed_rmse), 6),
    if (!is.null(best_model_based)) round(best_model_based$n_indiv) else "none found",
    if (!is.null(best_model_based)) round(best_model_based$loci) else "-",
    if (!is.null(best_model_based)) signif(ifelse(!is.null(best_model_based$abs_diff), best_model_based$abs_diff, best_model_based$predicted_rmse), 6) else "-"
  )
)

cat("\n\n=====================================================\n")
cat("           FULL ANALYSIS SUMMARY TABLE\n")
cat("=====================================================\n")
print(summary_table, row.names = FALSE)

write.csv(summary_table, "full_analysis_summary_table.csv", row.names = FALSE)
cat("\nSaved: full_analysis_summary_table.csv\n")

```

